\documentclass[12pt]{article}
\usepackage[margin=1in,landscape]{geometry}
\usepackage{multicol}
\author{Sara Bonisteel}
\title{Bananas Foster}
\date{}
\begin{document}
\begin{multicols*}{2}
\maketitle

Source: New York Times Cooking

\section{Notes}

The New York Times food editor Jane Nickerson first published this recipe in 1957 as part of an article on New Orleans-style Creole cooking. Adapted from Brennan's restaurant, this recipe is meant to be a showstopper. But it's deceptively easy. Be sure to have a lid at the ready to extinguish the flame in case things get out of hand. If you cannot find banana liqueur, just add a teaspoon more rum.

\section{Ingredients}

\begin{itemize}
    \item 1 tablespoon unsalted butter
    \item 2 teaspoons dark brown sugar
    \item 1 banana, peeled, halved lengthwise and crosswise
    \item Cinnamon
    \item 1 teaspoon banana liqueur
    \item 1 ounce light rum (80­ to 90 ­proof)
    \item Vanilla ice cream, for serving
\end{itemize}

\section{Method}

\begin{enumerate}
    \item Melt butter and sugar in a small frying pan. Add banana pieces and sauté over medium heat until lightly browned, turning pieces once. Sprinkle with cinnamon. Remove pan from heat.
    \item Add liqueur and rum to pan. To flambé, carefully light sauce with long-reach lighter. Spoon flaming sauce over the banana pieces until flame is extinguished.
    \item Serve warm banana pieces and sauce over vanilla ice cream.
\end{enumerate}

\end{multicols*}
\end{document}
