\documentclass[12pt]{article}
\usepackage[margin=1in,landscape]{geometry}
\usepackage{multicol}
\author{gingernuts13}
\title{Cinnamon Buns Fluffiest and Stickiest}
\date{}
\begin{document}
\begin{multicols*}{2}
\maketitle

Source: r/breadit

\section{Notes}

Pretty unfortunate title and author, but we'll see if it's tasty. Also the original text had a chronic lack of articles and grammar and all around good writing. Just salty.

\section{Ingredients}

\begin{itemize}
    \item \textbf{For the (kinda fake tbh) brioche:}
    \item 400g bread flour
    \item 170g milk
    \item 50g sugar
    \item 1 tsp. salt
    \item 1 tsp. vanilla
    \item 2 tsp. yeast
    \item 2 large eggs
    \item 60g oil
    \item \textbf{For the filling:}
    \item 1 cup packed brown sugar
    \item 3 tsp. cinnamon
    \item 2 tbsp. butter
    \item \textbf{For the icing:}
    \item 8 oz room temperature cream cheese
    \item 2 c. powdered sugar
    \item 1 stick softened butter
    \item heavy cream to thicken mixture
\end{itemize}

\section{Method}

\begin{enumerate}
    \item Pour all of the ingredients except oil into a mixing bowl.
    \item Mix on low until dough comes together, then add in oil until it combines.
    \item Knead the dough until it passes the window pane effect. Because this is a very enriched dough, may take 10 minutes or more in a stand mixer.
    \item Form a boule, and place it in a lightly oiled boil, and allow it to rise until doubled, or about one hour.
    \item While the dough is proofing, make the cinnamon filling.
    \item Remove the dough and flatten it out into a rectangle of about 12 inches x 15 inches.
    \item Spread evenly the filling, ``leaving about a 0.5 inch space on one edge to fold over'' (who knows what that means).
    \item Roll the rectangle up, and slice it into 14 rolls, then place those in a baking pan. Leave these until they have doubled in size.
    \item Bake for about 20 minutes at 350F.
    \item While baking, make the icing by creaming all ingredients together. Mix in some heavy cream until it is slightly thinned and will stiffly pour onto the buns.
    \item Let them cool slightly, then apply the cream cheese topping.
\end{enumerate}

\end{multicols*}
\end{document}
